Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 b

### 2018-05-04 ms.tex
added a few notes on resolution and added a better match between resolution of models and data.

We decided to re-visit the stellar parameters by examining the spectra taken with the High Definition Spectrograph (HDS) spectrograph on the Subaru telescope \citep{noguchi2002hds}.
There is one set of data taken on 2013-06-22 (UT) discussed in \citet{kawahara2013starspots}, including 4 exposures each 2700 seconds in duration.
Additionally, there are two set of observations from 2015-08-28 (UT) and 2015-08-29 (UT) that were taken to understand the kinematics of the system \citep{masuda2018rvKIC1255}, with exposure durations of 2400 seconds each.
The second set of observations happened after the reaction wheel failure on 2015-05-11\footnote{https://www.nasa.gov/mission\_pages/kepler/news/keplerm-20130521.html} that ended photometry of the main Kepler field, so no simultaneous Kepler photometry was available with the high dispersion spectroscopy.

@@

\subsection{Independent Reduction}
K Masuda independently reduced the \shStar\ Subaru data to examine if there could be an orbiting body on a highly eccentric star-grazing orbit that would reveal itself through radial velocity variations.
This more sophisticated reduction masks all telluric emission features and any outliers, producing cleaner spectra.
Time-variable outliers like cosmic rays are removed by measuring deviations from the median spectrum for the night.
The night-sky emissions from OH and O$_2$ are removed by using the \citet{osterbrock1996lineAtlas} night sky atlas.
All OH and O$_2$ lines are removed regardless if they are visible in the spectrum of \shStar.
Also, we found the median spectrum for the night (2015-05-11) to increase the signal to noise and perform outlier rejection.
The median spectrum is visible in Figure \ref{fig:mgTripletBOSZ}.

@@

\begin{figure}[!hbtp]
\begin{centering}
\includegraphics[width=0.45\textwidth]{images/subaru/bosz_mg_triplet.pdf}
\caption{Example spectrum of \shStar\ (reduced by Kento Masuda) near the Mg triplet compared to 4500 K BOSZ models with two different log(g)s.}\label{fig:mgTripletBOSZ}
\end{centering}
\end{figure}

>>>>

We decided to re-visit the stellar parameters by examining the spectra taken with the High Definition Spectrograph (HDS) spectrograph on the Subaru telescope \citep{noguchi2002hds}.
There is one set of data taken on 2013-06-22 (UT) discussed in \citet{kawahara2013starspots}, including 4 exposures each 2700 seconds in duration.
For this 2013 observation, the instrument was configured to use an image slicer unit \#2, which has a resolving power R$\approx$80,000.
Additionally, there are two set of observations from 2015-08-28 (UT) and 2015-08-29 (UT) that were taken to understand the kinematics of the system \citep{masuda2018rvKIC1255}, with exposure durations of 2400 seconds each.
The instrument 
The second set of observations happened after the reaction wheel failure on 2015-05-11\footnote{https://www.nasa.gov/mission\_pages/kepler/news/keplerm-20130521.html} that ended photometry of the main Kepler field, so no simultaneous Kepler photometry was available with the high dispersion spectroscopy.

@@

\subsection{Independent Reduction}
K Masuda independently reduced the \shStar\ Subaru data to examine if there could be an orbiting body on a highly eccentric star-grazing orbit that would reveal itself through radial velocity variations \citep{masuda2018rvKIC1255}.
This more sophisticated reduction masks all telluric emission features and any outliers, producing cleaner spectra.
Time-variable outliers like cosmic rays are removed by measuring deviations from the median spectrum for the night.
The night-sky emissions from OH and O$_2$ are removed by using the \citet{osterbrock1996lineAtlas} night sky atlas.
All OH and O$_2$ lines are removed regardless if they are visible in the spectrum of \shStar.
Also, we found the median spectrum for the night (2015-05-11) to increase the signal to noise and perform outlier rejection.
The median spectrum is visible in Figure \ref{fig:mgTripletBOSZ}.

@@

\begin{figure}[!hbtp]
\begin{centering}
\includegraphics[width=0.45\textwidth]{images/subaru/bosz_mg_triplet_median_spec_w_5000.pdf}
\caption{Median spectrum of \shStar\ (reduced by Kento Masuda) near the Mg triplet compared to 4500 K BOSZ models with two different log(g)s.}\label{fig:mgTripletBOSZ}
\end{centering}
\end{figure}
